---
title: "Titanic_R"
author: "Michael Wang"
date: "August 7, 2016"
output: html_document
---

Install necessary packages:
```{r}
setwd("~/GitHub/Kaggle/Titanic")
train <- read.csv("train.csv")
test <- read.csv("test.csv")

library(rpart)
library(randomForest)
library(party)
library(dplyr)
```

Make a dataframe that joins training and test sets:
```{r}
test$Survived = NA
df <- rbind(train, test)
```

Engineer the title feature:
```{r}
df <- df %>%
  mutate(
    Name = as.character(Name),
    Title = sapply(Name, FUN = function(x) {strsplit(x, split = '[,.]')[[1]][2]}),
    Title = sub(' ', '', Title)
  )
```

Combine the 'special names' into their less special forms:
```{r}
df <- df %>%
  mutate(
    Title = ifelse(Title %in% c('Mme', 'Mlle'), 'Mlle', Title),
    Title = ifelse(Title %in% c('Capt', 'Major', 'Sir'), 'Sir', Title),
    Title = ifelse(Title %in% c('Dona', 'Lady','the Countess', 'Jonkheer'), 'Lady', Title),
    Title = factor(Title)
  )
```

Create the family size variable:
```{r}
df$FamilySize <- df$SibSp + df$Parch + 1
```

Engineer the family variable:
```{r}
df <- df%>%
  mutate(
    Surname = sapply(Name, FUN = function(x) {strsplit(x, split = '[,.]')[[1]][1]}),
    FamilyID = paste(as.character(FamilySize), Surname, sep=""),
    FamilyID = ifelse(FamilySize <= 2, 'Small', FamilyID)
    )
```

Delete erroneously labeled families:
```{r}
famIDs <- data.frame(table(df$FamilyID))
famIDs <- famIDs[famIDs$Freq <= 2,]
df$FamilyID[df$FamilyID %in% famIDs$Var1] <- 'Small'
df$FamilyID <- as.factor(df$FamilyID)
```

Fill in missing ages:
```{r}
summary(df)
Agefit <- rpart(Age ~ Pclass + Sex + SibSp + Parch + Fare + Embarked + Title + FamilySize, 
                data = df[!is.na(df$Age),], method="anova")
df$Age[is.na(df$Age)] <- predict(Agefit, df[is.na(df$Age),])
```

Fill in missing Embarked/Fares:
```{r}
df$Embarked[df$Embarked == ''] = "S"
df$Embarked <- factor(df$Embarked)
df$Fare[which(is.na(df$Fare))] <- median(df$Fare, na.rm=TRUE)
```

Recreate training and test sets:
```{r}
train <- df[1:891,]
test <- df[892:1309,]
```

Run the model:
```{r}
set.seed(858)
fit <- cforest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID,
               data = train, controls=cforest_unbiased(ntree=2000, mtry=3)) 

Prediction <- predict(fit, test, OOB=TRUE, type = "response")
submit <- data.frame(PassengerId = test$PassengerId, Survived = Prediction)
write.csv(submit, file = "titanic_r.csv", row.names = FALSE)
```
